Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-27 main_paper.tex
Update and fix proof of Theorem 2
This commit gives the first plausible proof of Theorem 2, but there may
still be subtle errors.

\begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
  The random variables $Y_{i}, X_{i}$ are i.i.d.\ and
  there exists a positive number $\kappa_0$ such that the following
  conditions hold for all $x$ in the neighborhood
  $(-\kappa_{0},\kappa_{0})$ around zero:
  \begin{enumerate}
  \item $\E[Y_{i}^{4} \mid X_{i}=x]$ is bounded and the density of $X$
    is continuous and bounded away from zero.
  \item $\mu_{+}(x) = \E[ Y_{i}(1) \mid X_{i}=x ]$ and
    $\mu_{-}(x) = \E[ Y_{i}(0) \mid X_{i}=x ]$ are $p+2$ times
    continuously differentiable.
  \item $\sigma^{2}_{+}(x)=\V[ Y_{i}(1) \mid X_{i}=x ]$ and
    $\sigma^{2}_{-}(x)=\V[ Y_{i}(0) \mid X_{i}=x ]$ are continuous and
    bounded away from zero.
 \end{enumerate}
\end{assumption}

@@

\newpage\appendix
\section{Mathematical Appendix}
\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau_h - \Delta^*_h - \tau = (\hat\tau_h - \E \hat \tau_h) +
  (\E \hat \tau_h - \tau) - (\E^* \hat \tau^*_h - \tau^*)
\end{equation*}
The design of the bootstrap ensures that
\begin{align*}
  \label{eq:6}
  \E^* \hat\mu_{+}^*(h_n) - \mu_{+}^{*}
  &= h_n^{2} \mu_+^{*(2)} \Bf_{+}(h_n)/2,
  &\E^* \hat\mu_{-}^*(h_n) - \mu_{-}^{*}
  &= h_n^{2} \mu_-^{*(2)} \Bf_{-}(h_n)/2,
\end{align*}
almost surely, implying that
\begin{equation*}
  \label{eq:7}
    \E^* \hat\tau^{*}_h - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align}
  \hat\tau_h - & \E \hat\tau_h + (\E \hat\tau_h - \tau) - (\E^* \hat\tau^*_h - \tau^*)\notag \\
  \label{eq:8}
  &= \hat\tau_h - \E\hat\tau_h
   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
  &= \hat\tau_h - \E\hat\tau_h
   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2 \notag \\
  \label{eq:9}
  &\pushright{- h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b_n)$ and
$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b_n)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau_h - \E\hat\tau_h$,
$\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}$, and
$\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

\subsection{Proof of Theorem~\ref{T2}}
We can repeat the steps from Theorem~\ref{T1}'s proof to show that
\begin{align*}
  \hat\tau^* - \Delta^{**} - \tau^* &= (\hat\tau^* - \E^* \hat \tau^*) +
  (\E^* \hat \tau^* - \tau^*) - (\E^{**} \hat \tau^{**} - \tau^{**}) \\
  &= \hat\tau^* - \E^*\hat\tau^*
   + h_n^2 (\hat\mu_-^{*(2)}(b_n) - \mu_-^{*(2)}) \Bf_{-}(h_{n}) /2
   - h_n^2 (\hat\mu_+^{*(2)}(b_n) - \mu_+^{*(2)}) \Bf_{+}(h_{n}) / 2.
\end{align*}
Consequently, the asymptotic behavior of
$\hat\tau^* - \Delta^** - \tau^*$ is determined by the behavior of
$\hat\tau^* - \E^*\hat\tau*$ and
$\hat\mu_{\pm}^{*(2)} - \mu_\pm^{*(2)}$ and these random variables are
weighted averages of the sums
\begin{equation*}
  \sum_{i \in I^{\pm}(b_n)} Z_i \varepsilon_i^*
\end{equation*}
with $Z_i = (1, X_i, X_i^2)'$. By construction,
\begin{equation*}
  \V^*\Big(\ssum{i}{b_n} Z_i \varepsilon_i^* \Big)
  = \hat\sigma_\pm^2(b_n) \Gamma_\pm(b_n)
\end{equation*}
almost surely, making~\eqref{eq:4} a consequence of CCT's SA?.

For~\eqref{eq:5}, since $\hat\tau - \Delta^*$ is itself asymptotically
normal, it suffices to prove the pointwise result
\begin{equation}
  \label{eq:8}
  \Big\rvert \Pr^*[(\hat\tau^{*} - \Delta^{**} - \tau^*)
  / V^{1/2}(h_n,b_n) \leq x ] - \Phi(x)] \Big\lvert \to^p 0.
\end{equation}
for all $x$. Since the limiting distribution is continuous, an
argument attributed to Poly\'a immediately extends the pointwise
convergence result to the uniform result stated in~\eqref{eq:5}. (See
van der vaart, p. for the details of the argument.) But~\eqref{eq:8}
follows from Lemma~\ref{L1} as well, completing the proof.\qed

\subsection{Supporting results}

\begin{lemma}\label{L1}
  Define $Z_i = (1, X_i, X_i^2)$.  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{equation}
    \label{eq:9}
    \Big\rvert \Pr^*\Big[ \Gamma_\pm(b_n)^{-1/2}
    \sum_{i \in I^{\pm}(b_n)} Z_i \varepsilon_i^* / \hat\sigma_\pm(b_n) < x \Big]
    - \Phi(x) \Big\lvert \to^p 0.
  \end{equation}
\end{lemma}

\begin{proof}
  Let $z_i = \alpha' Z_i$ for an arbitrary nonzero $\alpha$ and define
  $\gamma_\pm(b_n) = \alpha'\Gamma_\pm(b_n)\alpha$. We will
  establsh asymptotic normality for the scalar $z_i \varepsilon_i^*$;
  the multivariate case follows via the Cram\'er-Wold device. (cite
  van der vaart.)

  Define the filtration
  \begin{equation}
    \label{eq:10}
    \Fc_j^{*\pm} = \sigma(Y_1,\dots,Y_n; X_1,\dots,X_n;
    \varepsilon_{i_1}^{*\pm},\dots,\varepsilon_{i_j}^{*\pm})
  \end{equation}
  where the values $i_1, i_2,\dots, i_{M_h^{\pm}}$ form an ordering of
  all of the elements of $I_n^\pm$. (The specific order is
  unimportant.) Then
  $\{z_{i_j} \varepsilon_{i_j}^{*\pm}, \Fc_j^{*\pm}\}$ is a martingale
  difference sequence and~\eqref{eq:9} holds if
  \begin{equation}
    \label{eq:11}
    \savg{i}{h} z_{i}^2 \varepsilon_{i}^{*\pm\,2} -
    \gamma_{\pm}^*(b_n) \hat\sigma
    \to^p 0
  \end{equation}
  and, for all
  $\delta > 0$,
  \begin{equation}
    \label{eq:12}
    \oavg{j}{h} z_{i_j}^2 \E^*( \varepsilon_{i_j}^{*\pm\,2}
    \1\{z_{i_j}^2 \varepsilon_{i_j}^{*\pm\,2} / M_h^\pm > \delta \}
    \mid \Fc_{j-1}^{\pm}) \to^p 0.
  \end{equation}
  (cite Hall and Heyde.)

  For~\eqref{eq:11}, observe that
  $\{z_{i_j}^2 (\varepsilon_{i_j}^{*2} - \hat\sigma^2_\pm(b_n)), \Fc_j^\pm\}$
  is also a martingale difference sequence so convergence follows from
  the LLN.

  For~\eqref{eq:12}, we have
  \begin{align*}
    \oavg{j}{h} z_{i_j}^2 \E^*( \varepsilon_{i_j}^{*\pm\,2}
    \1\{z_{i_j}^2 \varepsilon_{i_j}^{*\pm\,2} / M_h^\pm > \delta \}
    \mid \Fc_{j-1}^{\pm})
    &= \oavg{i}{h_n} z_i^2 \oavg{j}{b_n} \hat\varepsilon_{j}^{\pm 2}
      \1\{\hat\varepsilon_{j}^{\pm 2} > \delta M_n^{\pm} / z_i^2 \} \\
  \end{align*}
  (Finish with: $\varepsilon_i^2$ is uniformly integrable,
  $\hat\varepsilon_i^2$ gets arbitrarily close to $\varepsilon_i^2$)
\end{proof}

>>>>

\begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
  The random variables $Y_i, X_i$ are independent but not necessarily
  identically distributed. There exists a positive number $\kappa_0$
  such that the following conditions hold for all $x$ in the
  neighborhood $(-\kappa_{0},\kappa_{0})$ around zero:
  \begin{enumerate}
  \item $\E[Y_{i}^{4} \mid X_{i}=x]$ is bounded and the density of $X$
    is continuous and bounded away from zero.
  \item $\mu_{+}(x) = \E[ Y_{i}(1) \mid X_{i}=x ]$ and
    $\mu_{-}(x) = \E[ Y_{i}(0) \mid X_{i}=x ]$ are $p+2$ times
    continuously differentiable.
  \item $\sigma^{2}_{+}(x)=\V[ Y_{i}(1) \mid X_{i}=x ]$ and
    $\sigma^{2}_{-}(x)=\V[ Y_{i}(0) \mid X_{i}=x ]$ are continuous and
    bounded away from zero.
 \end{enumerate}
\end{assumption}

@@

\section{Proofs of mathematical results}
\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau_h - \Delta^*_h - \tau = (\hat\tau_h - \E \hat \tau_h) +
  (\E \hat \tau_h - \tau) - (\E^* \hat \tau^*_h - \tau^*)
\end{equation*}
The design of the bootstrap ensures that
\begin{align*}
  \label{eq:6}
  \E^* \hat\mu_{+}^*(h_n) - \mu_{+}^{*}
  &= h_n^{2} \mu_+^{*(2)} \Bf_{+}(h_n)/2,
  &\E^* \hat\mu_{-}^*(h_n) - \mu_{-}^{*}
  &= h_n^{2} \mu_-^{*(2)} \Bf_{-}(h_n)/2,
\end{align*}
almost surely, implying that
\begin{equation*}
  \label{eq:7}
    \E^* \hat\tau^{*}_h - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align}
  \hat\tau_h - & \E \hat\tau_h + (\E \hat\tau_h - \tau) - (\E^* \hat\tau^*_h - \tau^*)\notag \\
  &= \hat\tau_h - \E\hat\tau_h
   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
  &= \hat\tau_h - \E\hat\tau_h
   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2 \notag \\
  \label{eq:8}
  &\pushright{- h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b_n)$ and
$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b_n)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau_h - \E\hat\tau_h$,
$\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}$, and
$\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:8} to get
\begin{align*}
  \hat\tau_h^* - &\Delta_h^{**} - \tau^*
  = (\hat\tau^*_h - \E^* \hat \tau^*_h) +
  (\E^* \hat \tau^*_h - \tau^*) - (\E^{**} \hat \tau^{**}_h - \tau^{**}) \\
  &= \hat\tau^*_h - \E^*\hat\tau^*_h
   + h_n^2 (\hat\mu_-^{*(2)}(b_n) - \mu_-^{*(2)}) \Bf_{-}(h_{n}) /2
   - h_n^2 (\hat\mu_+^{*(2)}(b_n) - \mu_+^{*(2)}) \Bf_{+}(h_{n}) / 2 \\
  &= \Omega^{+}(b_n)' \epb_{+}^{*} - \Omega^{-}(b_n)' \epb_{-}^{*},
\end{align*}
where
$\epb_{+}^{*} =
(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_b^{+}}^{*})'$ and
$\Omega^{+}_b$ is an $M_b^{+}$-dimensional vector with $i$th element
$\Omega_{1i}^{+}(b_n) - \Omega_{2i}^{+}(b_n)$, which are defined as
\begin{align*}
  \Omega_{1i}^{+}(b) &=
  (1\quad 0)
  \Big(\ssum{j}{h_n} r_1(X_j / h_n) r_1(X_j / h_n)' \Big)^{-1}
    r_1(X_{m^+_i} / h_n) \1\{h_n > X_{m_i} \geq 0\}
\intertext{and}
  \Omega_{2i}^{+}(b) &=   (0\quad 0 \quad h_n^2) 
  \Big(\ssum{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m^+_i} / b).
\end{align*}
Here $r_p(x) = (1, x, x^2,\dots,x^{p})'$ and $m^+_i$ is the subsequence of
$1,2,\dots$ such that $0 \leq X_{m_i} < b$. The definitions of
$\epb_{-}^{*}$ and $\Omega^-(b_n)$ have the same definitons as
$\epb_{+}^{*}$ and $\Omega^+(b_n)$ after making the obvious
substitiutions of ``$-$'' for ``$+$.''

Given~\eqref{eq:8}, it suffices to prove that
\begin{gather}
  \label{eq:9}
  \rho(V^{-1/2}(h_n) \Omega^{+}(b_n)'\epb_{+}^{*},
    V^{-1/2}(h_n)\Omega^{+}(b_n)'\epb_{+}) \to^p 0
  \intertext{and}
  \label{eq:10}
  \rho(V^{-1/2}(h_n)\Omega^{-}(b_n)'\epb_{-}^{*},
    V^{-1/2}(h_n)\Omega^{-}(b_n)'\epb_{-}) \to^p 0
\end{gather}
with $\epb_+$ an i.i.d. random vector of length $M_b^+$, the $i$th
element of which is distributed as
\[
  \varepsilon_{i,+} =^d
  \begin{cases}
    Y_{m_1^+} - \E(Y_{m_1^+} \mid X_{m_1^+})
    & \text{with probability\ } 1/M_{b}^+ \\
    \vdots \\
    Y_{m_{M_b^+}^+} - \E(Y_{m_{M_b^+}^+} \mid X_{m_{M_b^+}^+})
    & \text{with probability\ } 1/M_{b}^+,
  \end{cases}
\]
$\epb_-$ the corresponding quantity after replacing ``+'' with ``--,'' and
$\rho$ the Mallows metric \citep{bickel1981}.\footnote{%
  For two random vectors $u$ and $v$ with finite 2nd moments, $\rho(u, v)$
  is defined as
  \begin{equation}
    \label{eq:11}
    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
  \end{equation}}

We will only prove~\eqref{eq:9} since the proof of~\eqref{eq:10} is
identical. By Theorem 2.1 of \cite{freedman1981}, we have
\begin{align*}
  \rho(V^{-1/2}(h_n) \Omega^{+}(b_n)'\epb_{+}^{*}, V^{-1/2}(h_n)&\Omega^{+}(b_n)'\epb_{+}) \\
  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
    \tr(V^{-1/2}(h_n) \Omega^{+}(b_n)' \Omega^{+}(b_n)V^{-1/2}(h_n)) \\
  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
\end{align*}
the second line holding as a consequence of CCT's Lemma SA1. So it suffices
to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
$\dot{\varepsilon}_i$ be an i.i.d. sequence randomly drawn from $\epb_+$
with replacement and let
$\bar{\varepsilon} = (1/M_b^{+}) \osum{i}{b_n} \dot{\varepsilon}_i$. Then,
using the same arguments as \cite{freedman1981}, we have the upper bound
\begin{equation}
  \label{eq:12}
  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
  \leq
  \bar\varepsilon^2 +
  (2/M_{b_n}^+) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
  + \rho(\dot\varepsilon_1, \varepsilon_{+,1}).
\end{equation}
But $\bar\varepsilon^2 \to^p 0$ by the LLN,
\[
  (1/M_{b_n}^+) \osum[+]{i}{b}
  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
\]
by CCT's Lemma SA1, and
$\rho(\dot\varepsilon_1, \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
\cite{bickel1981}.\qed
